Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-01-20 Grassmannian_cells.tex
Random edits

  The \emph{universal covering quiver} $\widetilde Q$ of $Q$ has vertices $\widetilde Q_0=Q_0\times W_Q$ and arrows $\widetilde Q_1=Q_1\times W_Q$, where $(\alpha,w):\big(s(\alpha),w\big)\to\big(t(\alpha),w\alpha\big)$ for $\alpha\in Q_1$ and $w\in W_Q$.
  Write $G_Q:\rep\widetilde Q\to\rep Q$ for the natural functor.

@@

\begin{lemma}
  Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and $\widetilde Q$.
\end{lemma}
\begin{proof}
  This statement is clear for the simple representations $S_i$, $i\in Q_0$.
  Now every preprojective or preinjective representation of $Q$ can be obtained by applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S'_j$ of a quiver $Q'$ whose underlying graph is the same as the one for $Q$.
  Applying a BGP-reflection to a fixed vertex $i$ of $Q$ corresponds to applying BGP-reflections to all vertices $(i,\chi)\in\hat Q_0$, where $\chi$ runs through all $\chi\in A_Q$ (resp. to all $(i,w)\in \tilde Q_0$ with $w\in W_Q$).
  This gives the claim.
\end{proof}

@@

Write $\Sigma_1$ and $\Sigma_2$ for the BGP-reflection functors of $K(n)$ \cite{bgp}. 
We use the same symbols $\Sigma_1$, $\Sigma_2$ for the BGP-reflection functors of $K(n)^{op}$, this should not lead to any confusion. 
Then the endofunctors $\Sigma_1^2$ and $\Sigma_2^2$ are each naturally isomorphic to the identity maps on the full subcategories $\rep_{\langle 1\rangle} K(n),\rep_{\langle 2\rangle} K(n)\subset \rep K(n)$, where the objects of $\rep_{\langle i\rangle} K(n)$ are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_2\Sigma_1$.

@@

  It is easy to see that $(l,1)$ is a Schur root since all indecomposable representations with this dimension vector have trivial endomorphism ring.
  Thus the roots $d(m,r)$ are also Schur roots.
  \sayD{This can also be seen as a consequence of Corollary~\ref{cor:indecomposable truncated}, would it be better if we reorganize?}
  It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite{sch}.
  This shows the second statement.

@@

For each $m\ge2$, there is an Auslander-Reiten sequence \cite[Section V]{ars}
\begin{equation}
  \label{eq:AR sequence}
  0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m\otimes H_m\stackrel{ev}{\longrightarrow} P_{m+1}\longrightarrow 0,
\end{equation}
where the right-hand morphism is the natural evaluation map.

\begin{lemma}
  \label{le:injective evaluation maps}
Let $m\geq 1$.  For any $V\in \Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
\end{lemma}
%%%%%%%%%%%%%%%%%%%
% needs polishing %
%%%%%%%%%%%%%%%%%%%
\begin{proof}\sayT{Maybe we can shorten the proof. I don't see a  proof which does not use reflection functors at the moment.}
  As $\Ext(P_m\otimes V,P_{m-1})=0$ and $\Hom(P_1,I_1)=0$, we obtain a commutative diagram 
  \[\xymatrix{0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0\\0 \ar[r] & P_{m-1}\ar@{=}[u]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar@{}[ur]|(.7){\urcorner} \ar[r]\ar[u]^{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar_{ev_V}[u] & 0 \ar[u]}\]
  in which we set $P_0=0$ and $I_l=0$ for $l\leq 0$.
  Since $\mathrm{id}_{P_1}\otimes \iota_V$ is injective, the snake lemma shows that $\ker ev_V=0$ for $m=1$ and thus $ev_V$ is injective in this case.

  In view of Remark~\ref{rem:reflection recursion}, it is enough for the case $m>1$ to show that the cokernel of $ev_V$ does not have a preinjective direct summand when $m=1$.
  Clearly the cokernel of $\mathrm{id}_{P_1}\otimes \iota_V$ is isomorphic to $P_1\otimes H_1/V$.
  Thus we obtain the following commutative diagram induced by the cokernels of the above vertical maps, note that the vertical maps below are surjective:
  \[\xymatrix{0\ar[r] & P_1\otimes H_1/V \ar[r] &K\ar[r]& I_{1}\ar[r]&0\\0 \ar[r]  & P_1\otimes H_1 \ar[u]\ar[r]^{ev} &P_{2}\ar[u] \ar[r] & I_{1}\ar@{=}[u]\ar[r]&0.}\]

@@

\begin{lemma}
  \label{le:unique morphisms}
  Consider $V,W\in \Gr(H_m)$, $m\ge1$.
  \begin{enumerate}
    \item There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
    \item For $W\subset V$, we have $\Ext(P_{m+1}^W,P_{m+1}^V)\cong W^*\otimes(H_m/V)$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  We apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V)\longrightarrow \Ext(P_{m+1}^W,P_{m+1}^V)\longrightarrow 0.\]
  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$. 
  In this case, there is an isomorphism 
  \[\Ext(P_{m+1}^W,P_{m+1}^V)\cong\Hom(P_m\otimes W,P_{m+1}^V)\cong W^*\otimes H_m/V,\]
  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
\end{proof}

@@

\begin{lemma}
  \label{le:basic homological properties}
  For $V\in \Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
\end{lemma}
\begin{proof}
  Recall that $\Hom(X,P_\ell)\ne0$ (resp. $\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp. $1\le r\le\ell-2$).
  However, $P_{m+1}^V$ cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
  %Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0$.
\end{proof}

@@

\begin{lemma}
  \label{le:truncated extensions}
  For $V\in \Gr(H_m)$, $m\ge1$, we have $\Ext(P_{m+1}^V,P_m)\cong V^*$, where each nontrivial extension naturally corresponds to a codimension 1 subspace $U\subset V$. 
  More precisely, each element of $\Ext(P_{m+1}^V,P_m)$ corresponds to an exact sequence
  \[\xymatrix{0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0},\]
where $U\subset V$ satisfies $\dim(V/U)=1$.
\end{lemma}
\begin{proof}
  Consider a nonzero map $\varphi\in V^*$ and set $U=\ker\varphi\subset V$.
  There is a natural isomorphism $V^*\cong\Hom(P_m\otimes V,P_m)$ which takes $\varphi$ to $id\overline{\otimes}\varphi$.
  This gives rise to the following commutative diagram:
  \[\xymatrix{ & 0 \ar[d] & 0 \ar[d] & & \\
    & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes U \ar[d] & & \\
    0 \ar[r] & P_m\otimes V \ar[d]^{id\overline{\otimes}\varphi}\ar[r]\ar@{}[dr]|(.7){\lrcorner}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1} \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar@{=}[d] & 0\\
    0 \ar[r] & P_m \ar[r]\ar[d] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r] & 0\\
   & 0 & 0 & & }\]
  By Lemma~\ref{le:basic homological properties}, we may apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get the isomorphism 
  \[\Ext(P_{m+1}^V,P_m)\cong\Hom(P_m\otimes V,P_m)\cong V^*.\]
  Under this isomorphism, the functional $\varphi$ corresponds to the lower pushout sequence in the above diagram.
\end{proof}

@@

For $V\in \Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
\sayD{The next results need some serious clean-up, can they be proven for $K(n)$ without passing to the universal cover?}
\begin{lemma}
  For $V\in \Gr(H_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
  Moreover, the upper pullback sequence
  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  splits for every proper subspace $W\subsetneq V$.
\end{lemma}
\begin{proof}
  We proceed by simultaneous induction on $m$ and $\codim_{H_m} V$.

  When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{H_m} V,1)$.
  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le l$ which gives both claims in this case.

@@

It will be rather important that the lifts $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.
Indeed, recall that the group $W_n$ naturally acts on $\widetilde{K(n)}_0$ via translation, i.e. $w.(i,w')=(i,ww')$, and this induces an action of $W_n$ on $\rep\widetilde{K(n)}$.
Following the notation of Section~\ref{sec:covering}, we write $\tilde P_{m,w}$ for the representation of $\widetilde{K(n)}$ obtained by translating the lifted preprojective representation $\tilde P_m$ by the action of $w\in W_n$.
To simplify the notation, we abbreviate $P_{2l-1,i}:=P_{2l-1,\alpha_i}$ and $P_{2l,i}:=P_{2l,\alpha_i^{-1}}$.
\begin{lemma}
  For each $m\ge2$, the representation $\tilde P_m$ has precisely $n$ subrepresentations covering $P_{m-1}$.
  These are the representations $P_{m-1,i}$ corresponding the $n$ different arrows of $K(n)$. 
\end{lemma}
\begin{proof}
  This is clear for $m=2$ and follows in general by applying the identities \eqref{eq:recursive covers}.
\end{proof}
\begin{remark}
  Note that the dimension vectors of the lifted preprojectives $\tilde P_m$ are symmetric.
  In particular, they all have the same middle vertex $(1,1)$ if $m$ is odd and middle vertex $(2,1)$ if $m$ is even.
\end{remark}
Let
$$I^n_l:=\{(j_1,\ldots,j_{l})\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
As we fixed the number of arrows, we drop the $n$ in what follows.

With every sequence of natural numbers $\ui=(i_1,\ldots,i_k)$ with $i_j\leq n$ and $k\leq m-1$, we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$. More detailed, we obtain a sequence of preprojective representations 
$$\tilde P_{m-k,\ui}\subset \tilde P_{m-k+1,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-2,(i_1,i_2)}\subset \tilde P_{m-1,i_1}\subset\tilde P_{m}.$$

\begin{lemma}
  \label{le:homdecomposition}
  \sayT{I split up some lemmas. Check references}
  Let $m\geq 2$. The following holds:
  \begin{enumerate}
    \item We have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional. 
    \item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
      \begin{align}
        \label{ses1}
        \ses{\bigoplus_{i=1}^l \tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}}.
      \end{align}
    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have 
      $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=0=\Ext(\tilde P_{m,i},\tilde P_{m,k}).$$
  \end{enumerate}
\end{lemma}
\begin{proof}
  The first part is immediate from Theorem \ref{covering}.
  Now the observations of Section \ref{sec:truncated preprojectives} immediately yield the second part.
  The last part is also a consequence of Theorem \ref{covering}.
  Indeed, for $1\leq k\leq n$, we have 
  $$\CC=\Hom_Q(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m,i},\tilde P_{m,k}).$$
  But $\Hom_{\tilde Q}(\tilde P_{m,k},\tilde P_{m,k})\cong\CC$ and so we must have $\Hom_{\tilde Q}(\tilde P_{m,i},\tilde P_{m,k})=0$ for $i\neq k$.
  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,k})$ follows in the same manner using that $P_m$ is exceptional.
\end{proof}
In the following, we make use of this lemma and fix a basis of $\Hom(P_{m-1},P_m)$ which is compatible with this direct sum decomposition.
Note that, we can quotient out the lifted preprojectives successively, i.e. we have short exact sequences
\[\ses{ \tilde P_{m-1,j_l}}{\tilde P^{(j_1,\ldots,j_{l-1})}_m}{\tilde P_{m}^{\uj}}.\]
\begin{lemma}
  \label{le:properties}
  \sayD{Parts (2) and (3) should follow directly from Lemma~\ref{le:unique morphisms} and the definition of truncated preprojectives for $K(n)$.} 
  For $m\geq 2$ and $\uj\in I_l$, the following hold:
  \begin{enumerate}
    \item We have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\CC$  for $k\neq j_i$ for $i=1,\ldots,l$. 
    \item We have $\Hom(\tilde P_m,\tilde P_m^{\uj})=\CC$ and $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$. 
    \item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.
  \end{enumerate}
\end{lemma} 
\begin{proof}
  The first identity of the last statement follows when applying $\Hom(\tilde P_{m-1,k},-)$ to the short exact sequence (\ref{ses1}) using the results of Lemma \ref{le:homdecomposition}.

>>>>

  The \emph{universal covering quiver} $\widetilde Q$ of $Q$ has vertices $\widetilde Q_0=Q_0\times W_Q$ and arrows $\widetilde Q_1=Q_1\times W_Q$, where $(\alpha,w):\big(s(\alpha),w\big)\to\big(t(\alpha),w\alpha\big)$\sayD{Should we write $\alpha w$ here so that arrows act of the left and compose as functions?} for $\alpha\in Q_1$ and $w\in W_Q$.
  Write $G_Q:\rep\widetilde Q\to\rep Q$ for the natural functor.

@@

\begin{lemma}
  Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and to $\widetilde Q$.
\end{lemma}
\begin{proof}
  This statement is clear for the simple representations $S_i$, $i\in Q_0$.
  Now every preprojective or preinjective representation of $Q$ can be obtained by applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S'_j$ of a quiver $Q'$ whose underlying graph is the same as the one for $Q$.
  Applying a BGP-reflection to a fixed vertex $i$ of $Q$ corresponds to applying BGP-reflections to all vertices $(i,\chi)\in\hat Q_0$, where $\chi$ runs through all $\chi\in A_Q$ (resp. to all $(i,w)\in \tilde Q_0$ with $w\in W_Q$).
  This gives the claim.
\end{proof}

@@

Write $\Sigma_1$ and $\Sigma_2$ for the BGP-reflection functors of $K(n)$ \cite{bgp}. 
We use the same symbols $\Sigma_1$, $\Sigma_2$ for the BGP-reflection functors of $K(n)^{op}$, this should not lead to any confusion. 
Then each endofunctor $\Sigma_i^2$ is naturally isomorphic to the identity map on the full subcategory $\rep_{\langle i\rangle} K(n)\subset \rep K(n)$ whose objects are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
In particular, $\Sigma_i$ gives an exact equivalence of categories $\Sigma_i:\rep_{\langle i\rangle} K(n)\to\rep_{\langle i\rangle} K(n)^{op}$.
Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_2\Sigma_1$.

@@

  It is easy to see that $(l,1)$ is a Schur root since all indecomposable representations with this dimension vector have trivial endomorphism ring.
  Thus the roots $d(m,r)$ are also Schur roots.
  \sayD{This can also be seen as a consequence of Corollary~\ref{cor:indecomposable truncated}, would it be better if we reorganize?}
  It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite[Theorem 2.2]{sch}.
  This shows the second statement.

@@

For each $m\ge2$, there is an Auslander-Reiten sequence (cf.\ \cite[Section V]{ars})
\begin{equation}
  \label{eq:AR sequence}
  0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m\otimes H_m\stackrel{ev}{\longrightarrow} P_{m+1}\longrightarrow 0,
\end{equation}
where the right-hand morphism is the natural evaluation map.

\begin{lemma}
  \label{le:injective evaluation maps}
  For any $V\in \Gr(H_m)$, $m\geq 1$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
\end{lemma}
%%%%%%%%%%%%%%%%%%%
% needs polishing %
%%%%%%%%%%%%%%%%%%%
\begin{proof}\sayT{Maybe we can shorten the proof. I don't see a  proof which does not use reflection functors at the moment.}
  As $\Ext(P_m\otimes V,P_{m-1})=0$ and $\Hom(P_1,I_1)=0$, we obtain a commutative diagram 
  \[\xymatrix{0 \ar[r] & P_{m-1}\ar@{=}[d]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar@{}[dr]|(.7){\lrcorner} \ar[r]\ar[d]_{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar_{ev_V}[d] & 0 \ar[d]\\ 0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0}\]
  in which we set $P_0=0$ and $I_l=0$ for $l\leq 0$.
  Since $\mathrm{id}_{P_1}\otimes \iota_V$ is injective, the snake lemma shows that $\ker ev_V=0$ for $m=1$ and thus $ev_V$ is injective in this case.

  In view of Remark~\ref{rem:reflection recursion}, it is enough for the case $m>1$ to show that the cokernel of $ev_V$ does not have a preinjective direct summand when $m=1$.
  Clearly the cokernel of $\mathrm{id}_{P_1}\otimes \iota_V$ is isomorphic to $P_1\otimes H_1/V$.
  Thus we obtain the following commutative diagram induced by the cokernels of the above vertical maps, note that the vertical maps below are surjective:
  \[\xymatrix{0 \ar[r]  & P_1\otimes H_1 \ar[d]\ar[r]^{ev} &P_{2}\ar[d] \ar[r] & I_{1}\ar@{=}[d]\ar[r]&0\\ 0\ar[r] & P_1\otimes H_1/V \ar[r] &K\ar[r]& I_{1}\ar[r]&0.}\]

@@

\begin{lemma}
  \label{le:unique morphisms}
  Consider $V,W\in \Gr(H_m)$, $m\ge1$.
  \begin{enumerate}
    \item There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
    \item For $W\subset V$, we have $\Ext(P_{m+1}^W,P_{m+1}^V)\cong W^*\otimes(H_m/V)$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  We apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V)\longrightarrow \Ext(P_{m+1}^W,P_{m+1}^V)\longrightarrow 0.\]
  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$. 
  In this case, there are isomorphisms
  \[\Ext(P_{m+1}^W,P_{m+1}^V)\cong\Hom(P_m\otimes W,P_{m+1}^V)\cong W^*\otimes H_m/V,\]
  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
\end{proof}

@@

\begin{lemma}
  \label{le:basic homological properties}
  For $V\in\Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
\end{lemma}
\begin{proof}
  Recall that $\Hom(X,P_\ell)\ne0$ (resp. $\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp. $1\le r\le\ell-2$).
  However, $P_{m+1}^V$ cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
  %Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0$.
\end{proof}

\begin{lemma}
  For $V\in\Gr(H_m)$, $m\ge1$, the representation $\Sigma_2(P_{m+1}^V)^\sigma$ is also truncated preprojective.
\end{lemma}
\begin{proof}
  Apply the functor $\Sigma_2(-)^\sigma$ to the sequence \eqref{eq:truncated preprojectives}.
\end{proof}

@@

\begin{lemma}
  \label{le:truncated extensions}
  For $V\in \Gr(H_m)$, $m\ge1$, we have $\Ext(P_{m+1}^V,P_m)\cong V^*$, where each nontrivial extension naturally corresponds to a codimension 1 subspace $U\subset V$. 
  More precisely, each element of $\Ext(P_{m+1}^V,P_m)$ corresponds to an exact sequence
  \[\xymatrix{0 \ar[r] & P_m \ar[r] & P_{m+1}^U \ar[r] & P_{m+1}^V \ar[r] & 0},\]
where $U\subset V$ satisfies $\dim(V/U)=1$.
\end{lemma}
\begin{proof}
  Consider a nonzero map $\varphi\in V^*$ and set $U=\ker\varphi\subset V$.
  There is a natural isomorphism $V^*\cong\Hom(P_m\otimes V,P_m)$ which takes $\varphi$ to $id\overline{\otimes}\varphi$.
  This gives rise to the following commutative diagram:
  \[\xymatrix{ & 0 \ar[d] & 0 \ar[d] & & \\
    & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes U \ar[d] & & \\
    0 \ar[r] & P_m\otimes V \ar[d]^{id\overline{\otimes}\varphi}\ar[r]\ar@{}[dr]|(.7){\lrcorner}\ar@{}[dr]|(.3){\ulcorner} & P_{m+1} \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar@{=}[d] & 0\\
    0 \ar[r] & P_m \ar[r]\ar[d] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r] & 0\\
   & 0 & 0 & & }\]
  But observe that we may apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get the isomorphism 
  \[\Ext(P_{m+1}^V,P_m)\cong\Hom(P_m\otimes V,P_m)\cong V^*.\]
  Under this isomorphism, the functional $\varphi$ corresponds to the lower pushout sequence in the above diagram.
\end{proof}

@@

For $V\in \Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
\sayD{The next results need some serious clean-up, can they be proven for $K(n)$ without passing to the universal cover?}
\begin{lemma}
  For $V\in \Gr(H_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
  Moreover, the upper pullback sequence
  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  splits for every proper subspace $W\subsetneq V$.
\end{lemma}
\begin{proof}
  For the first claim, we proceed by induction on $m$.
  When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{H_m} V,1)$.
  In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le l$.

@@

It will be rather important that our chosen lifts $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.
Indeed, recall that the group $W_n$ naturally acts on $\widetilde{K(n)}_0$ via translation, i.e. $w.(i,w')=(i,ww')$, and this induces an action of $W_n$ on $\rep\widetilde{K(n)}$.
Following the notation of Section~\ref{sec:covering}, we write $\tilde P_{m,w}$ for the representation of $\widetilde{K(n)}$ obtained by translating the lifted preprojective representation $\tilde P_m$ by the action of $w\in W_n$.
To simplify the notation, we abbreviate $\tilde P_{2l-1,i}:=\tilde P_{2l-1,\alpha_i}$ and $\tilde P_{2l,i}:=\tilde P_{2l,\alpha_i^{-1}}$.
\begin{lemma}
  For each $m\ge2$, the representation $\tilde P_m$ has precisely $n$ subrepresentations covering $P_{m-1}$.
  These are the representations $\tilde P_{m-1,i}$ corresponding to the $n$ different arrows of $K(n)$. 
\end{lemma}
\begin{proof}
  This is clear for $m=2$ and follows in general by applying the identities \eqref{eq:recursive covers}.
\end{proof}
\begin{remark}
  Note that the dimension vectors of the lifted preprojectives $\tilde P_m$ are symmetric.
  In particular, they all have the same middle vertex $(1,1)$ if $m$ is odd and middle vertex $(2,1)$ if $m$ is even.
\end{remark}

Recall that $n\ge3$ is fixed.
Set
\[I_l:=\{(j_1,\ldots,j_l)\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.\]
With every sequence of natural numbers $\ui=(i_1,\ldots,i_k)$ with $i_j\leq n$ and $k\leq m-1$, we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$. More detailed, we obtain a sequence of preprojective representations 
$$\tilde P_{m-k,\ui}\subset \tilde P_{m-k+1,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-2,(i_1,i_2)}\subset \tilde P_{m-1,i_1}\subset\tilde P_{m}.$$

\begin{lemma}
  \label{le:homdecomposition}
  \sayT{I split up some lemmas. Check references}
  Let $m\geq 2$. The following holds:
  \begin{enumerate}
    \item We have $\Hom_{K(n)}(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\widetilde{K(n)}}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\widetilde{K(n)}}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional.
    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have 
      \[\Hom(\tilde P_{m,i},\tilde P_{m,k})=0=\Ext(\tilde P_{m,i},\tilde P_{m,k}).\]
    \item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
      \begin{align}
        \label{ses1}
        \ses{\bigoplus_{i=1}^l \tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}}.
      \end{align}
  \end{enumerate}
\end{lemma}
\begin{proof}
  The first part is immediate from Theorem~\ref{covering}.
  The second part is also a consequence of Theorem~\ref{covering}.
  Indeed, for $1\leq k\leq n$, we have 
  $$\CC=\Hom_Q(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m,i},\tilde P_{m,k}).$$
  But $\Hom_{\tilde Q}(\tilde P_{m,k},\tilde P_{m,k})\cong\CC$ and so we must have $\Hom_{\tilde Q}(\tilde P_{m,i},\tilde P_{m,k})=0$ for $i\neq k$.
  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,k})$ follows in the same manner using that $P_m$ is exceptional.
  Now the observations of Section~\ref{sec:truncated preprojectives} immediately yield the final claim.
\end{proof}
In the following, we make use of this lemma and fix a basis of $\Hom(P_{m-1},P_m)$ which is compatible with this direct sum decomposition.
Note that we can quotient out the lifted preprojectives successively, i.e. we have short exact sequences
\[\ses{ \tilde P_{m-1,j_l}}{\tilde P^{(j_1,\ldots,j_{l-1})}_m}{\tilde P_{m}^{\uj}}.\]
\begin{lemma}
  \label{le:properties}
  \sayD{Parts (2) and (3) should follow directly from Lemma~\ref{le:unique morphisms} and the definition of truncated preprojectives for $K(n)$.} 
  For $m\geq 2$ and $\uj\in I_l$, the following hold:
  \begin{enumerate}
    \item We have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\CC$  for $k\neq j_i$ for $i=1,\ldots,l$. 
    \item We have $\Hom(\tilde P_m,\tilde P_m^{\uj})=\CC$ and $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$. 
    \item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.
  \end{enumerate}
\end{lemma} 
\begin{proof}
  The first identity of the last statement follows when applying $\Hom(\tilde P_{m-1,k},-)$ to the short exact sequence (\ref{ses1}) using the results of Lemma \ref{le:homdecomposition}.
